Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-08 p2/conclusion.tex
New section on multiple directory values; reorganizing section

An extension of our results could also entail relaxing
the simplifying assumptions we used.
% TODO TODO TODO
Identifying which results depend on the assumption that $|\setd|=1$
and devising updated proofs and algorithms for when $|\setd|>1$,
or specifying a pre-processing step that reconciles meta-information in directories
can enable the synchronizer
to identify and resolve a wider range of conflicts.

Similarly, designing pre- and post-processors that
present removing and creating a node
not as separate updates but as a single rename (move),
could contribute to the user-friendliness of the reconciler
and help avoid human error.

>>>>

An extension of our results could also entail relaxing
the simplifying assumptions we used.
The model and algorithms could be extended to the $|\setd|>1$ case, % TODO write this
to enable the synchronizer
to identify and resolve a wider range of conflicts.
Also, pre- and post-processors could be designed that
reconcile meta-information in directories or encode them as files, % TODO write this
or present removing and creating the same content at a different node
not as separate updates but as a single rename (move).
These could contribute to the user-friendliness of the reconciler
and help avoid human error.

### 2018-07-08 p2/def-filesystem.tex
New section on multiple directory values; reorganizing section

An essential assumption in our model is that there is only
a \emph{single directory value} ($|\setd|=1$).
The realisation that
this creates a symmetry between directories and empty nodes
that allows formulating a correct and complete reconciliation algorithm
is one of the main contributions of this paper.
This assumption does not hinder the applicability of our results
(in fact, many real-life synchronizers make the same assumption),
but makes it possible to exploit a hidden symmetry in filesystem commands.

% TODO To avoid the proliferation of edge cases
% TODO In appendix TODO we describe why it can be a sensible choice
% TODO for actual synchronizers, and we also present an encoding that makes it possible
% TODO to extend our results to the $|\setd|>1$ case.

% % We do this because, as Bill Zissimopoulos pointed 
% % out \cite{BZ},
% % we often do not want to consider metadata stored in
% % directories (e.g. permission settings) during synchronization,
% % as these are not generally understood well by users,
% % and, if needed, conflict resolution on these settings can be easily automated.
% % We will also see that this assumption makes it possible
% % to define a maximal reconciliation algorithm.

>>>>

An essential assumption in our model is that there is only
a \emph{single directory value} ($|\setd|=1$).
The realisation that
this creates a symmetry between directories and empty nodes
and makes it possible to exploit a hidden symmetry in filesystem commands
that allows formulating a correct and complete reconciliation algorithm
is one of the main contributions of this paper.

This assumption does not hinder the applicability of our results.
In fact, commercial designs for synchronizers 
often avoid considering metadata in directories as % TODO expand
as these are generally not understood well by users,
and, if needed, conflict resolution on these settings can be easily automated
\cite{BZ}.

### 2018-07-08 p2/intro.tex
New section on multiple directory values; reorganizing section

The paper is organised as follows.
We start by defining a model of filesystems and a set of commands
that we will use to describe updates and modifications in \cref{sec_def}.
This is followed by investigating the properties and behaviors
of command pairs in \cref{section_axioms}.
\Cref{sec_update} describes update detection and ordering filesystem commands.
The main result of this section if that under some simple conditions,
a set of filesystem commands executed in any feasible order leads
to the same changes in the filesystem.
The reconciliation and conflict detection algorithm is defined in
\cref{sec_rec}, which merges two sets of commands.
We then proceed to prove that the output of reconciliation
is correct in the sense that 
it can be applied to the replicas without causing an error,
and it is maximal
inasmuch as no further updates can be applied under any circumstances.
In order to be able to do this, we introduce
domains of sets of command sequences,
and show that it has a number of highly convenient properties.
\Cref{sec_relatedwork,sec_algebra,sec_conclusion}
discuss related work, comparing our results to other research,
outlining directions for further work
on the introduced algebraic system, and provide the conclusion.
\Cref{axiom_proof} contains technical proofs for propositions on the behavior of command pairs.

>>>>

The paper is organised as follows.
%
We start by defining a model of filesystems and a set of commands
that we will use to describe updates and modifications in \cref{sec_def}.
%
This is followed by investigating the properties and behaviors
of command pairs in \cref{section_axioms}.
%
\Cref{sec_update} describes update detection and ordering filesystem commands.
The main result of this section if that under some simple conditions,
a set of filesystem commands executed in any feasible order leads
to the same changes in the filesystem.
%
The reconciliation and conflict detection algorithm is defined in
\cref{sec_rec}, which merges two sets of commands.
We then proceed to prove that the output of reconciliation
is correct in the sense that 
it can be applied to the replicas without causing an error,
and it is maximal
inasmuch as no further updates can be applied under any circumstances.
In order to be able to do this, we introduce
domains of sets of command sequences,
and show that it has a number of highly convenient properties.
%
\Cref{sec_multidir,sec_algebra,sec_conclusion}
describe extending our model to widen its applicability;
outline directions for further work on the introduced algebraic system,\
and provide the conclusion.
%
We discuss related work, comparing our results to other research in \cref{sec_relatedwork},
while
\cref{axiom_proof} contains technical proofs for propositions on the behavior of command pairs.

### 2018-07-08 p2/paper.tex
Proofs for the rules
Restating rules for proofs
Improved introduction
Updated notation
Process todos
Resolve TODOs
New section on multiple directory values; reorganizing section

\input{macros}

@@

TODO: $n'$ should always be parent(n).

TODO: Theorem 1, S' extends S. ... All S is extended by simple sequence, and generate with inference rules.

TODO: Explain what happens to FF commands.

TODO: $|[D]|=1$ - where used? Can we move $A \cap B$ to the beginning?

% A: <D1,D2,n'>
% B: <D1,D3,n'> <empt,F,n>
% Reconciliation does not create file, but we can create it -> reconciliation maximal not true.

TODO: After reconciliation, subsequence order works.

@@

@@

% TODO Add reviewer
% TODO Consider below
I thank L. Csirmaz for his invaluable input on this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.

@@

>>>>

\input{macros}
\input{axiom-def}

@@

@@

%section
\input{multidir}

@@

I thank L.~Csirmaz for his invaluable input on this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
I am indebted to the anonymous reviewers of the previous version of this paper
for their helpful and detailed remarks
that helped improve the presentation of the paper
and make it accessible for a wider audience.

@@

\appendix

\section{Proofs for Rules}\mlabel{axiom_proof}
\input{axiom-proof}
